---
title: "Migration flows chord diagram"
author: "Duc-Quang Nguyen"
date: "15 Aug 2016"
output: 
  html_document:
    toc: true
    toc_depth: 3
    theme: journal
---
##

"Refugee crisis", "migrant waves" such terms routinely headline European medias (including ours). If it is undeniable that It turns out global migration is in decline and only 0.5% of the world's population has left their country over the last 5 years.



We showed in a previous story the international migrant figures from the United Nations. Some impressive large numbers, 244 millions migrants worldwide, 3.3% of the global population. These data represent however the migrant stocks, meaning it is the cumulated number of foreign-born people by country in 2015. 
From these numbers one cannot distinghish an exchange student abroad for a year or somebody who has been living there for 40 years. 

Fortunately researchers at the Vienna Institute of Demography in Austria have devised a method published in Science to infer how many people migrated from which country to which country and there were able to do for different periods in time. 



Guy J. Abel, a professor from the Asian Demographic Research Institute, Shanghai University & Vienna Institute of Demography was kind enough to share some of his latest data with swissinfo. 

Fortunately researchers at the . Using data from published, show that global migration has remained at a steady level over half a century. Furthermore, global migration has actually decreased 





http://www.global-migration.info





## Data

### Main sources
* [Nikola Sander, Guy J. Abel & Ramon Bauer ](http://www.global-migration.info)
* [Data wrapped into a R package and procedures](https://gjabel.wordpress.com/2016/05/18/updated-circular-plots-for-directional-bilateral-migration-data/)
* [research paper](data/WP2016_02.pdf)

### Related data
  * Issue: data is not completely disaggretated - origin other North & other South
  * [UN population division - International migrant stock - By destination and origin](http://www.un.org/en/development/desa/population/migration/data/estimates2/estimates15.shtml), xls saved in data 
  * [Read the doc about the data & methodology](data/MigrationStockDocumentation_2015.pdf)

## Related stories
* [Le monde flux de migrants](http://www.lemonde.fr/planete/article/2014/05/29/230-millions-de-migrants-dans-le-monde-des-flux-qui-ne-cessent-d-augmenter_4428870_3244.html)
* [Spiegel Global Migration? Actually, The World Is Staying Home](http://www.spiegel.de/international/world/why-global-migration-statistics-do-not-add-up-a-1090736.html)
* ['We don't know nearly enough about migration'](http://phys.org/news/2016-05-dont-migration.html)
* [Most Conventional Wisdom About Refugees and Immigration Is Wrong](http://www.fastcoexist.com/3060766/most-conventional-wisdom-about-refugees-and-immigration-is-wrong)
* [scientificamerican Global Migrant Flows: An Interactive Map](http://blogs.scientificamerican.com/observations/global-migrant-flows-an-interactive-map/)


## Text snippets
* [from](https://www.fastcoexist.com/3060766/most-conventional-wisdom-about-refugees-and-immigration-is-wrong)
  * More people migrate within Europe than come to Europe from Africa, for instance
  * And people don’t really move from the poorest to the richest countries. Instead, the trend is for people to move to a country that is a little better off than where they’re coming from.
* [IOM factsheet](https://www.iom.int/news/iom-releases-global-migration-trends-2015-factsheet)  
  * South-South migration flows (across developing countries) continued to grow compared to South-North movements (from developing to developed countries.) In 2015, 90.2 million international migrants born in developing countries were living in other countries in the Global South, while 85.3 million born in the South lived in countries in the Global North.
* [Spiegel](http://www.spiegel.de/international/world/why-global-migration-statistics-do-not-add-up-a-1090736.html)
  * The number of people worldwide who left their native countries in the last five years.  36.5 million, or 0.5 percent of the world's population. All others, or 99.5 percent of the global population, are non-migrants, or people who were living in the same country in 2015 as in 2010
  * "The truth," says Guy Abel, "is that the global migration dynamic has remained constant at a low level for more than half a century."
  * According to Abel, "244 million is a number that says nothing about how many people migrated from which country to which country, and when."
  * "The general perception of migration suffers from a Eurocentric worldview. People believe that the entire world wants to go to Europe. But when you look at our graphics, you quickly realize that this isn't true."
  * For one thing, according to the UN's definition, the 244 million correspond to the total aggregated migrant stock in the world. This means that anyone who ever left their country of birth and is still alive is part of this number
  * The largest global migrant flows take place within individual world regions, not across continents. This is evidenced by the thickest arrows in the chart, which point from Africa to Africa, from the Middle East to the Middle East, and from East Asia to East Asia. The arrows represent the migrations of hundreds of thousands of people from places like India to Dubai or from Syria to Lebanon.
  * Migration paths do not lead primarily from very poor to very rich countries, but rather adhere to a graduated model. "People move to countries where the economy is somewhat stronger than in their native country," says Sander. She means from Bangladesh to India or from Zimbabwe to South Africa, for example.
  * The number of migrating migrants between 2010 and 2015 (36.5 million) is more than 8 million fewer than in the previous five-year period (45 million). The global migration rate reached an historic peak between 1990 and 1995, a time when the Iron Curtain had fallen, Afghanistan had descended into civil war and there was genocide in Rwanda. The 0.5 percent figure for the last five years is the smallest value since 1960.
  * There appears to be a historic rule of thumb," says Abel, "which is that for every five-year period, six out of 1,000 people are on the move." This stability is also apparent even if one does not count those who are currently migrating, but rather all people who have been living outside their native country for any period of time, as the UN does. In that case, migrants have made up about 3 percent of the world population since 1960

# Code

### Packages & settings

```{r setup, include=FALSE}
translation.file <- "input/Global migration flow, 2010-2015 - chord diagram - Sheet1.csv"


#install.packages("migest")
library(migest)
library(circlize)
library(readr)
library(tidyr)
library(dplyr)
library(magrittr)
library(countrycode)
library(ggplot2)
library(scales)
library(swiMap)
library(extrafont)

### Interactive 
library(htmltools)
library(htmlwidgets)
library(swiRcharts)
```

### Load & wrangle data

Based on R code by [Guy Abel's migest](https://github.com/gjabel/migest/blob/master/demo/cfplot_reg2.R)

```{r load & wrangle data}

## load translation
txt <- read.csv(translation.file, row.names = 1, stringsAsFactors = F, na.strings = "NAN")
# discard incomplete translations
cidx <- unique(which(txt =="" | is.na(txt), T)[,2])
if(length(cidx > 0)) {
  warning(paste(colnames(txt)[cidx], collapse = "\t"), " languages will be discarded!", "\n")
  txt <- txt[,-cidx, drop = F]
}
colnames(txt)

regions <- data.frame(
  name = c(
    "Eastern Europe & Central Asia", "Europe", "Africa",
    "Eastern Asia", "Southern Asia", "Western Asia",
    "Oceania", "Northern America", "Latin America & Caribbean"
  ), 
  code = c("EECA", "E", "A", "EA", "SA", "WA", "O", "NA", "LAC"),
  color = c('#ac7f3e', '#336666', '#666633', 
            '#ab3d3f', '#996666', '#ac673e', 
            '#663333', '#333366', '#366096')
)

```

```{r static cord diagram}

## Load data 
# df0 the bidirectional flow data
df0 <- read.csv(system.file("vidwp", "reg_flow.csv", package = "migest"), stringsAsFactors=FALSE)

# the metadata
df <- read.csv(system.file("vidwp", "reg_plot.csv", package = "migest"), stringsAsFactors=FALSE)

# overwrite colors
idx <- match(regions$name, df$region)
if(any(is.na(idx))) stop()
df$col1 <- as.character(regions[idx, 'color'])
df$code <- regions[idx, 'code']  


for (lang in colnames(txt)) {

  chord.path <- paste0("output/chordDiagram_" , lang, ".png")
  html.out <- paste0("chord_migration_", lang, ".html")
  font.family <-  txt["font.family", lang]
  title.family <- txt["title.family", lang]
  
  df1 <- df
  df1$region <- txt[as.character(df1$code), lang]
  df1 <- df1[match( c('NA', 'A', 'E','EECA', 'WA', 'SA', 'EA', 'O', 'LAC'), df1$code),]
    
  df2 <- df0
  df2$orig_reg <- txt[as.character(regions[match(df2$orig_reg, regions$name), 'code']), lang]
  df2$dest_reg <- txt[as.character(regions[match(df2$dest_reg, regions$name), 'code']), lang]
  
  ## Create the static graphic
  png(chord.path,  res = 200, pointsize = 9, height = 1100 * 1.1, 
        width = 1100 * 1.1)
  
  par(mar=c(0,0,0,0), family = font.family)
  chordDiagram(x = df2, grid.col = df1$col, transparency = 0.25,
    order = df1$region, directional = 1,
    direction.type = c("arrows", "diffHeight"), diffHeight  = -0.04,
    annotationTrack = "grid", annotationTrackHeight = c(0.05, 0.1),
    link.arr.type = "big.arrow", link.sort = TRUE, link.largest.ontop = TRUE)
      
  circos.trackPlotRegion(
    track.index = 1, 
    bg.border = NA, 
    panel.fun = function(x, y) {
      xlim = get.cell.meta.data("xlim")
      sector.index = get.cell.meta.data("sector.index")
      reg = df1$region[df1$region == sector.index]
      color =  df1$col1[df1$region == sector.index]
        
      circos.text(x = mean(xlim), y = 4.1, col = color,
                  labels = reg, facing = "bending", cex = 1, family = title.family)
      circos.axis(h = "top", 
                  major.at = seq(0, xlim[2], by = ifelse(test = xlim[2]>10, yes = 2, no = 1)), 
                  minor.ticks = 1, major.tick.percentage = 0.5, labels.cex = 0.6,
                  labels.niceFacing = FALSE)
    }
  )
  dev.off()

  ## HTMLize 
  footer <- paste0(
    txt['source', lang], ": ", htmlLink(txt['source.url', lang], txt['source.name', lang]), " | ",
    txt['code', lang], ": ", htmlLink(txt['code.url', lang], txt['code.name', lang]), " | ",
    htmlLink("http://www.swissinfo.ch", 'swissinfo.ch')               
  )
  descr <- paste0(txt["descr1", lang])
  
  save_html(
    tags$html(
      tags$head(includeHTML("styles.html")),
      tags$body(
        h2(HTML(txt["title1", lang])),
        div(class = "descr", HTML(descr)),
        p(
          invisible(sapply(1:nrow(regions), function (i) {
            HTML(
              paste0(div(class = "tooltip", 
                HTML(paste0(' <h5> ', txt[as.character(regions[i, 'code']), lang], " </h5> ")), 
                span(class="tooltiptext", HTML(
                '<img src="', paste0(regions[i, 'code'], "_map.png"), 
                '" alt="', paste0("Map ", as.character(regions[i, 'code'])) , 
                '" style="width:160;height:160px;">'))
            )))   
          }, simplify = F))
        ),
        p(HTML("<br>")),
        div(img(src = basename(chord.path), width= "100%")),
        div(id = "cite", HTML(footer)),
        HTML(iframeresizer)
      )), file = html.out, libdir = "js"
  )
  
     # move stuff
    fileToMove <- c(html.out)
    file.rename(from = fileToMove, to = paste0("output/", fileToMove))
 
 
}

```